Product plots

### 2011-06-23 reviews/response.txt

Other changes:

* Rather than eliminating the section describing the R implementation altogether, we have expanded it slightly to give a taste of how it might be used.

* Where appropriate, figures labelled with distributional decomposition.

* We wish we could make the figures larger and the labels easier to read, but the page limits are extremely tight this year.  We have done our best to ensure that all information is convey redundantly through colour or description in the captions.

### 2011-06-23 prodplots-infovis.tex
More minor changes

Area plots correspond to tilings of the (2d) plane. We could consider partitions of higher-d spaces (e.g. 3d or 4d), but given that we have to project these down to 2d for viewing on paper or screen, there is little disadvantage to working directly in 2d. There are many possible ways to tile the plane, so to weed these down to a manageable number, we identify  constraints, in the style of \citep{keim:2002}, that are important for visualising counts.

@@

We are also exploring the connection between product plots and log-linear (aka Poisson) models, the statistical models most commonly used for count data. Some special cases of the general connection have already been worked out. For example, \citep{hofmann:2003} shows how looking for straight lines in a mosaic plot corresponds to a formal test of independence between two variables. Generally, we are interested in knowing what visual comparisons are equivalent to what formal statistical tests, and conversely, how significant coefficients in a model can help us choose a set of useful plots. Generally, given a question, can we suggest appropriate plots? Or given a plot, can we suggest questions that it might answer?

>>>>

Area plots correspond to tilings of the (2d) plane. We could consider partitions of higher-d spaces (e.g. 3d or 4d), but given that we have to project these down to 2d for viewing on paper or screen, there is little disadvantage to working directly in 2d. There are many possible ways to tile the plane, so to cut these down to a manageable number, we identify  constraints, in the style of \citep{keim:2002}, that are important for visualising counts.

@@

We are also exploring the connection between product plots and log-linear (aka Poisson) models, the statistical models most commonly used for count data. Some special cases of the general connection have already been worked out. For example, \citep{hofmann:2003} shows how looking for straight lines in a mosaic plot corresponds to a formal test of independence between two variables. Generally, we are interested in knowing what visual comparisons are equivalent to what formal statistical tests, and conversely, how significant coefficients in a model can help us choose a set of useful plots. Given a question, can we suggest appropriate plots? Given a plot, can we suggest questions that it might answer?
